---
title: "Adjusted Analyses within Subpopulations"
author: "JAS, building off code by Mehr"
date: "4/19/2024"
output: html_document
---

```{r setup, include=FALSE}
# install.packages("sandwich")
# install.packages("lmtest")
library(sandwich)
library(lmtest)

knitr::opts_chunk$set(echo = TRUE)
```
# Instructions for Creating Needed Code

Subpopulation Analyses only run for Phase 1 40% Subset


2. Need to  replace pollutant variable so there is one set for each of four pollutants. Variable names are:
bc_avg2
no2_avg5
pm_avg1
o3_avg1

3. Need to repeat code for each outcome. Outcomes are:
ards
dialysis
pneumo
vent

Remember the final object that stores the RR and CI for a given model should include the pollutant, outcome and population so that later we can combine them all into a table.


Adding stratified models for comorbidities
*** 


#A Run Data Processing Script
```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Kannoth/Programs/Final Code/Data Processing.R")
```

## Function 1

For subpopulations not defined by comorbidities (age, race, ethnicity)

```{r}
calculate_adj_model_strat <- function(outcome, pollutant, phase_data) {
  # Fit Poisson regression model
  model <- glm(formula(paste(outcome, "~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}
```

##Function 2

For subpopulations defined by comorbidities (asthma, diabetes, hypertension)
```{r}
calculate_adj_model_strat_asthma <- function(outcome, pollutant, phase_data) {
  # Fit Poisson regression model
  model <- glm(formula(paste(outcome, "~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ diabetes + hyper")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}

  calculate_adj_model_strat_diab<- function(outcome, pollutant, phase_data) {
  # Fit Poisson regression model
  model <- glm(formula(paste(outcome, "~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke) + hyper+asthma")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
  }
  
  calculate_adj_model_strat_hyper<- function(outcome, pollutant, phase_data) {
  # Fit Poisson regression model
  model <- glm(formula(paste(outcome, "~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ diabetes + asthma")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}
```

## Running for all combinations 

Note that results match original models run without functions-JAS
```{r}

all_objects<-ls()

subpop.df.all<-all_objects[grep("_40cov_", all_objects)]
subpop.df.demo<-subpop.df.all[!grepl("asthma|diabetes|hyper|nevi|headings", subpop.df.all)]

subpop.df.demo<-subpop.df.demo[sapply(subpop.df.demo, function(x) is.data.frame(get(x)))]


result_df <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(subpop.df.demo)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.demo[phase])
      output <- calculate_adj_model_strat(outcomes[outcome], pollutants[pollutant], data)
      
      result_df <- rbind(result_df, data.frame(PhaseData = subpop.df.demo[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df

subpop.df<-all_objects[grep("_40cov_", all_objects)]
subpop.df.asthma<-subpop.df[grepl("asthma", subpop.df)]
subpop.df.hyper<-subpop.df[grepl("hyper", subpop.df)]
subpop.df.diab<-subpop.df[grepl("diab", subpop.df)]

result_df_asthma <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(subpop.df.asthma)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.asthma[phase])
      output <- calculate_adj_model_strat_asthma(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_asthma <- rbind(result_df_asthma, data.frame(PhaseData = subpop.df.asthma[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_asthma

result_df_hyper <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(subpop.df.hyper)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.hyper[phase])
      output <- calculate_adj_model_strat_hyper(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_hyper <- rbind(result_df_hyper, data.frame(PhaseData = subpop.df.hyper[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_hyper

result_df_diab <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(subpop.df.diab)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.diab[phase])
      output <- calculate_adj_model_strat_diab(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_diab <- rbind(result_df_diab, data.frame(PhaseData = subpop.df.diab[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_diab

```

## Function for Survival Outcomes

```{r}
calculate_adjsurvival_strat <- function(duration, outcome, pollutant, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  model <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper")), 
               data = phase_data, 
               ties = "breslow")
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model))
  CI <- exp(confint(model))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}

calculate_adjsurvival_strat_asthma <- function(duration, outcome, pollutant, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  model <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ diabetes + hyper")), 
               data = phase_data, 
               ties = "breslow")
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model))
  CI <- exp(confint(model))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}

calculate_adjsurvival_strat_diab <- function(duration, outcome, pollutant, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  model <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + hyper")), 
               data = phase_data, 
               ties = "breslow")
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model))
  CI <- exp(confint(model))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}

calculate_adjsurvival_strat_hyper <- function(duration, outcome, pollutant, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  model <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes")), 
               data = phase_data, 
               ties = "breslow")
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model))
  CI <- exp(confint(model))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}

```


## Running for all combinations 

```{r}
result_df_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = subpop.df.demo
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1") 
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adjsurvival_strat(duration, outcomes[outcome], pollutants[pollutant], data)
      
      result_df_s <- rbind(result_df_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[1,2],
                                               lower_95CI = output[1,6],
                                               upper_95CI = output[1,7]))
    }
  }
}

result_df_s

result_df_asthma_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = subpop.df.asthma
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1") 
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adjsurvival_strat_asthma(duration, outcomes[outcome], pollutants[pollutant], data)
      
      result_df_asthma_s <- rbind(result_df_asthma_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[1,2],
                                               lower_95CI = output[1,6],
                                               upper_95CI = output[1,7]))
    }
  }
}

result_df_asthma_s

result_df_hyper_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = subpop.df.hyper
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1") 
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adjsurvival_strat_hyper(duration, outcomes[outcome], pollutants[pollutant], data)
      
      result_df_hyper_s <- rbind(result_df_hyper_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[1,2],
                                               lower_95CI = output[1,6],
                                               upper_95CI = output[1,7]))
    }
  }
}

result_df_hyper_s

result_df_diab_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = subpop.df.diab
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1") 
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adjsurvival_strat_diab(duration, outcomes[outcome], pollutants[pollutant], data)
      
      result_df_diab_s <- rbind(result_df_diab_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[1,2],
                                               lower_95CI = output[1,6],
                                               upper_95CI = output[1,7]))
    }
  }
}

result_df_diab_s
```

## Run Models for Dialysis (Requires different population, excluding those who had received dialysis previously)

```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Kannoth/Programs/Final Code/Data Processing2.R")

result_df_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("dialysis") 

for (phase in 1:length(subpop.df.demo)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.demo[phase])
      output <- calculate_adj_model_strat(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_d <- rbind(result_df_d, data.frame(PhaseData = subpop.df.demo[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_d


result_df_asthma_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

for (phase in 1:length(subpop.df.asthma)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.asthma[phase])
      output <- calculate_adj_model_strat_asthma(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_asthma_d <- rbind(result_df_asthma_d, data.frame(PhaseData = subpop.df.asthma[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_asthma_d

result_df_hyper_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

for (phase in 1:length(subpop.df.hyper)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.hyper[phase])
      output <- calculate_adj_model_strat_hyper(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_hyper_d <- rbind(result_df_hyper_d, data.frame(PhaseData = subpop.df.hyper[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_hyper_d

result_df_diab_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)


for (phase in 1:length(subpop.df.diab)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(subpop.df.diab[phase])
      output <- calculate_adj_model_strat_diab(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_diab_d <- rbind(result_df_diab_d, data.frame(PhaseData = subpop.df.diab[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_diab_d

```



## Export in excel workbook

```{r}
require(openxlsx)
list_dataframes <- list("strat_demo" = result_df, "strat_asthma" = result_df_asthma, "strat_hyper"=result_df_hyper, "strat_diab"=result_df_diab, "strat_demo_s" = result_df_s, "strat_asthma_s" = result_df_asthma_s, "strat_hyper_s"=result_df_hyper_s, "strat_diab_s"=result_df_diab_s,"strat_demo_d" = result_df_d, "strat_asthma_d" = result_df_asthma_d, "strat_hyper_d"=result_df_hyper_d, "strat_diab_d"=result_df_diab_d)
write.xlsx(list_dataframes, file = "Stratified_results.xlsx")
```

