---
title: "Adjusted Analyses-Interactions"
author: "JAS, building off code by Mehr"
date: "2/12/2024"
output: html_document
---

```{r setup, include=FALSE}
# install.packages("sandwich")
# install.packages("lmtest")
library(sandwich)
library(lmtest)

knitr::opts_chunk$set(echo = TRUE)
```
# Instructions for Creating Needed Code

Initial code for one outcome, one pollutant during Phase1 is included below. We need crude models for the rest of th pollutants, phases and subsets. Then, they will need to be compiled into a Table for the Supplement.

Using the example code, you can cut/paste and replace the pollutant, dataset and rename output objects so that all can be output together into a file.

1. Need to copy code and replace dataset for different phases and different subsets. Datasets are 

coxph_phase1_df: Phase 1, full population
coxph_phase2and3_df: Phase 23, full population
coxph_phase1_40cov: Phase 1, 40% subset
coxph_phase2and3_40cov: Phase 2 and 3 40%subset

2. Need to copy code and replace pollutant variable so there is one set for each of four pollutants. Variable names are:
bc_avg2
no2_avg5
pm_avg1
o3_avg1

3. Need to repeat code for each outcome. Outcomes are:
ards
dialysis
pneumo
vent

Remember the final object that stores the RR and CI for a given model should include the pollutant, outcome and phase/population so that later we can combine them all into a table.
*** 


#A Run Data Processing Script
```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Jeanette_final/Data Processing.R")
```

## Function

```{r}
calculate_adj_model_int <- function(outcome, pollutant, phase_data) {
  # Fit Poisson regression model
  model.adj <- glm(formula(paste(outcome, "~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model.adj, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model.adj, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result.1 <- as.data.frame(cbind(RR, CI))
  result.1 <- cbind(as.data.frame(rownames(result.1)), result.1)
  names(result.1)[2] <- "RR"
  
 Estimate = result.1[2, "RR"]
  lwr = result.1[2, "2.5 %"]
  upr = result.1[2, "97.5 %"]
  result.2<-cbind(Estimate, lwr, upr)
  
  model.adj.int <- glm(formula(paste(outcome, "~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper", "+", pollutant, "*nevi")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
test_interaction <- (as.data.frame(anova(model.adj,model.adj.int, test = "Chisq")))[2,5]


model.adj.int2 = glm(formula(paste(outcome, "~", pollutant, "+ nevi_tertiles + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper", "+", pollutant, "*nevi_tertiles")), 
               data = phase_data, 
               family = poisson(link = "log"))

Result_LowNevi<-glht(model.adj.int2, linfct=t(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)), vcov=sandwich) #Confirmed that adding vcov=sandwich will ensure correct CIs when using confint
#Confirmed that it doesn't matter where in model the interaction is placed, the coefficients will always be at the end after all of the main effects

Result_LowNEVI_CI<-confint(Result_LowNevi)
Result_LowNEVI_est<-exp(Result_LowNEVI_CI[[9]])

Result_MedNevi<-glht(model.adj.int2, linfct=t(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0)), vcov=sandwich) 

Result_MedNEVI_CI<-confint(Result_MedNevi)
Result_MedNEVI_est<-exp(Result_MedNEVI_CI[[9]])

Result_HighNevi<-glht(model.adj.int2, linfct=t(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)), vcov=sandwich) 

Result_HighNEVI_CI<-confint(Result_HighNevi)
Result_HighNEVI_est<-exp(Result_HighNEVI_CI[[9]])

result.3<-rbind(result.2, Result_LowNEVI_est, Result_MedNEVI_est, Result_HighNEVI_est)
labels<-data.frame(c("Adj", "NEVI-T1", "NEVI-T2", "NEVI-T3"))
colnames(labels)<-"label"
result.3<-cbind(labels, result.3)
result<-list(2)
result[[1]]<-result.3
result[[2]]<-test_interaction

  return(result)
}

```


### Test chunk
output matches prior version 2/12
```{r}
output <- calculate_adj_model_int("ards", "no2_avg5", coxph_phase1_df)
```


## Running for all combinations 

Note that results match original models run without functions
```{r}
result_df <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adj_model_int(outcomes[outcome], pollutants[pollutant], data)
      
      result_df <- rbind(result_df, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               output[[2]],
                                               output[[1]]))
    }
  }
}

result_df
```

## Function for Survival Outcomes

```{r}
calculate_adjsurvival_model <- function(duration, outcome, pollutant, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  
    model.1 <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+asthma + diabetes + hyper")), 
               data = phase_data, 
               ties = "breslow")
    
      # Store coefficients and CIs
  HR <- exp(coeftest(model.1, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model.1, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result.1 <- as.data.frame(cbind(HR, CI))
  result.1 <- cbind(as.data.frame(rownames(result.1)), result.1)
  names(result.1)[2] <- "HR"
  
 Estimate = result.1[1, "HR"]
  lwr = result.1[1, "2.5 %"]
  upr = result.1[1, "97.5 %"]
  result.2<-cbind(Estimate, lwr, upr)
  
  model.2 <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+asthma + diabetes + hyper+", pollutant, "*nevi")), 
               data = phase_data, 
               ties = "breslow")
  
test_interaction <- (as.data.frame(anova(model.1,model.2, test = "Chisq")))[2,4]

  model.3 <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi_tertiles + age + factor(sex) + factor(bmi_cat) + factor(smoke)+asthma + diabetes + hyper+", pollutant, "*nevi_tertiles")), 
               data = phase_data, 
               ties = "breslow")
  
Result_LowNevi <-glht(model.3, linfct=t(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)), vcov=sandwich) #Confirmed that adding vcov=sandwich will ensure correct CIs when using confint
#Confirmed that it doesn't matter where in model the interaction is placed, the coefficients will always be at the end after all of the main effects

Result_LowNEVI_CI <-confint(Result_LowNevi )
Result_LowNEVI_est <-exp(Result_LowNEVI_CI[[9]])

Result_MedNevi <-glht(model.3, linfct=t(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0)), vcov=sandwich) 

Result_MedNEVI_CI <-confint(Result_MedNevi )
Result_MedNEVI_est <-exp(Result_MedNEVI_CI[[9]])

Result_HighNevi <-glht(model.3, linfct=t(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)), vcov=sandwich) 

Result_HighNEVI_CI <-confint(Result_HighNevi )
Result_HighNEVI_est <-exp(Result_HighNEVI_CI[[9]])

result.3<-rbind(result.2, Result_LowNEVI_est, Result_MedNEVI_est, Result_HighNEVI_est)

labels<-data.frame(c("Adj", "NEVI-T1", "NEVI-T2", "NEVI-T3"))
colnames(labels)<-"label"
result.3<-cbind(labels, result.3)
result<-list(2)
result[[1]]<-result.3
result[[2]]<-test_interaction


  return(result)
}
```

### Test chunk

Matches original output 2/12

```{r}
#output <- calculate_adjsurvival_model("hospital_days", "death", "no2_avg5", coxph_phase1_df)
```

## Running for all combinations 

```{r}
result_df_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1") 
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adjsurvival_model(duration, outcomes[outcome], pollutants[pollutant], data)
      
      result_df_s <- rbind(result_df_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               output[[2]],
                                               output[[1]]))
    }
  }
}

result_df_s
```


## Run Models for Dialysis (Requires different population, excluding those who had received dialysis previously)

```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Kannoth/Programs/Final Code/Data Processing2.R")

result_df_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("dialysis") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adj_model_int(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_d <- rbind(result_df_d, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               output[[2]],
                                               output[[1]]))
    }
  }
}

result_df_d
```



## Export in excel workbook

```{r}
require(openxlsx)
list_dataframes <- list("morbidity" = result_df, "dialysis" = result_df_d, "survival"=result_df_s)
write.xlsx(list_dataframes, file = "Adjusted_results_int.xlsx")
```

