---
title: "Categorical Poll Analysis"
author: "Sneha Kannoth"
date: "2025-01-16"
output: html_document
---

# Purpose of the Code

This code runs adjusted models where the air pollutant modeled concentrations are operationalized as quartiles. This allows assessment of linearity.

# A Run Data Processing Script

User input of path to data processing script

```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Jeanette_final/Data Processing.R")
```

## Function for Table 3 Analyses (Categorical AP)

```{r}
calculate_adj_model <- function(outcome, pollutant, phase_data) {
  # Fit Poisson regression model
  model <- glm(formula(paste(outcome, "~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}
```


## Running for all combinations 

Note that results match original models run without functions
```{r}
result_df <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_quartiles", "no2_quartiles", "pm_quartiles", "o3_quartiles")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adj_model(outcomes[outcome], pollutants[pollutant], data)
      
      result_df <- rbind(result_df, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               Q2_RR = output[2, "RR"],
                                               Q2_lower_95CI = output[2, "2.5 %"],
                                               Q2_upper_95CI = output[2, "97.5 %"],
                                               Q3_RR = output[3, "RR"],
                                               Q3_lower_95CI = output[3, "2.5 %"],
                                               Q3_upper_95CI = output[3, "97.5 %"],
                                               Q4_RR = output[4, "RR"],
                                               Q4_lower_95CI = output[4, "2.5 %"],
                                               Q4_upper_95CI = output[4, "97.5 %"]))
    }
  }
}

result_df
```

## Function for Survival Outcomes

```{r}
calculate_adjsurvival_model <- function(duration, outcome, pollutant, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  model <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper")), 
               data = phase_data, 
               ties = "breslow")
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model))
  CI <- exp(confint(model))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}
```


## Running for all combinations 

```{r}
result_df_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_quartiles", "no2_quartiles", "pm_quartiles", "o3_quartiles") 
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adjsurvival_model(duration, outcomes[outcome], pollutants[pollutant], data)
      
      result_df_s <- rbind(result_df_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               Q2_RR = output[1,2],
                                               Q2_lower_95CI = output[1,6],
                                               Q2_upper_95CI = output[1,7],
                                               Q3_RR = output[2,2],
                                               Q3_lower_95CI = output[2,6],
                                               Q3_upper_95CI = output[2,7],
                                               Q4_RR = output[3,2],
                                               Q4_lower_95CI = output[3,6],
                                               Q4_upper_95CI = output[3,7]))
    }
  }
}

result_df_s
```

## Run Models for Dialysis (Requires different population, excluding those who had received dialysis previously)

Note includes user-input to path to data processing specific for dialysis

```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Jeanette_final/Data Processing2.R")

result_df_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_quartiles", "no2_quartiles", "pm_quartiles", "o3_quartiles")
outcomes = c("dialysis") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adj_model(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_d <- rbind(result_df_d, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               Q2_RR = output[2, "RR"],
                                               Q2_lower_95CI = output[2, "2.5 %"],
                                               Q2_upper_95CI = output[2, "97.5 %"],
                                               Q3_RR = output[3, "RR"],
                                               Q3_lower_95CI = output[3, "2.5 %"],
                                               Q3_upper_95CI = output[3, "97.5 %"],
                                               Q4_RR = output[4, "RR"],
                                               Q4_lower_95CI = output[4, "2.5 %"],
                                               Q4_upper_95CI = output[4, "97.5 %"]))
    }
  }
}

result_df_d
```


## Export in excel workbook

```{r}
require(openxlsx)
list_dataframes <- list("adj_poisson" = result_df, "adj_poisson_dial" = result_df_d, "adj_survival"=result_df_s)
write.xlsx(list_dataframes, file = "CategoricalAP_Results.xlsx")
```

