---
title: "Crude Analyses"
author: "Mehr Shafiq w/ additions by JAS"
date: "2024-01-30"
output: html_document
---

```{r setup, include=FALSE}
# install.packages("sandwich")
# install.packages("lmtest")
library(sandwich)
library(lmtest)

knitr::opts_chunk$set(echo = TRUE)
```
# Purpose of Code

The following code constructs crude models for pollutants, phases and subsets. 

1. Populations are 

coxph_phase1_df: Phase 1, full population
coxph_phase2and3_df: Phase 23, full population
coxph_phase1_40cov: Phase 1, 40% subset
coxph_phase2and3_40cov: Phase 2 and 3 40%subset

2. Variable names for pollutants are:
bc_avg2
no2_avg5
pm_avg1
o3_avg1

3. Outcomes are:
ards
dialysis
pneumo
vent

Remember the final object that stores the RR and CI for a given model should include the pollutant, outcome and phase/population so that later we can combine them all into a table.
*** 


#A Run Data Processing Script
User Input for Path to Data Processing Script
```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Jeanette_final/Data Processing.R")
```

## Function for Crude Modified Poisson Models

```{r}
calculate_crude_model <- function(outcome, pollutant, phase_data) {
  # Fit Poisson regression model
  model <- glm(formula(paste(outcome, "~", pollutant)), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}
```

## Running for all combinations 

```{r}
result_df <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_crude_model(outcomes[outcome], pollutants[pollutant], data)
      
      result_df <- rbind(result_df, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df
```

## Function for Survival Outcomes

```{r}
calculate_survival_model <- function(duration, outcome, pollutant, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  model <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant)), 
               data = phase_data, 
               ties = "breslow")
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model))
  CI <- exp(confint(model))
  
  # Create a data frame with RR and CIs
  result <- as.data.frame(cbind(RR, CI))
  result <- cbind(as.data.frame(rownames(result)), result)
  names(result)[2] <- "RR"
  
  return(result)
}
```

## Running for all combinations 

```{r}
result_df_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1") 
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_survival_model(duration, outcomes[outcome], pollutants[pollutant], data)
      
      result_df_s <- rbind(result_df_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output$RR,
                                               lower_95CI = output$`2.5 %`,
                                               upper_95CI = output$`97.5 %`))
    }
  }
}

result_df_s
```

## Run Crude Models for Dialysis (Requires different population, excluding those who had received dialysis previously)

```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Jeanette_final/Data Processing2.R")

result_df_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1", "o3_avg1")
outcomes = c("dialysis") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_crude_model(outcomes[outcome], pollutants[pollutant], data)
      
      result_df_d <- rbind(result_df_d, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               RR = output[2, "RR"],
                                               lower_95CI = output[2, "2.5 %"],
                                               upper_95CI = output[2, "97.5 %"]))
    }
  }
}

result_df_d
```



## Export in excel workbook

```{r}
require(openxlsx)
list_dataframes <- list("crude_poisson" = result_df, "crude_poisson_dial" = result_df_d, "crude_survival"=result_df_s)
write.xlsx(list_dataframes, file = "Crude_Poisson_results.xlsx")
```

