---
title: "MultipollutantModels"
author: "JAS"
date: "2024-01-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Purpose of Code

Construct adjusted models that mutually adjust for two pollutants. Due to high correlations between pollutants, only run with ozone as second pollutant


# A Run Data Processing Script
```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Jeanette_final/Data Processing.R")
```

# B Function

```{r models}
calculate_adj_model_multipoll <- function(outcome, pollutant1, pollutant2, phase_data) {
  # Fit Poisson regression model
  model.adj <- glm(formula(paste(outcome, "~", pollutant1, "+", pollutant2, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+ asthma + diabetes + hyper")), 
               data = phase_data, 
               family = poisson(link = "log"))
  
  # Store coefficients and CIs
  RR <- exp(coeftest(model.adj, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model.adj, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result.1 <- as.data.frame(cbind(RR, CI))
  result.1 <- cbind(as.data.frame(rownames(result.1)), result.1)
  names(result.1)[2] <- "RR"
  
 Estimate = result.1[2, "RR"]
  lwr = result.1[2, "2.5 %"]
  upr = result.1[2, "97.5 %"]
  
   Estimate2 = result.1[3, "RR"]
  lwr2 = result.1[3, "2.5 %"]
  upr2 = result.1[3, "97.5 %"]
  
  result.2<-cbind(Estimate, lwr, upr, Estimate2, lwr2, upr2)
  
  return(result.2)
}

#check
#output<-calculate_adj_model_multipoll("ards", "pm_avg1", "o3_avg1", coxph_phase1_40cov)

```

# C Run for combinations
Note calls to functions require user input of phases, pollutants and outcomes.

```{r}
result_df <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants1 = c("bc_avg2", "no2_avg5", "pm_avg1")
pollutant2=c("o3_avg1")
outcomes = c("ards", "pneumo", "vent") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants1)) {
      data = get(phases_data[phase])
      output <- calculate_adj_model_multipoll(outcomes[outcome], pollutants1[pollutant], pollutant2, data)
      
      result_df <- rbind(result_df, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant1 = pollutants1[pollutant],
                                               Pollutant2=pollutant2,
                                               output
                                               ))
    }
  }
}

result_df
```


# D Function for Survival Outcomes

```{r}
calculate_adjsurvival_model_multipoll <- function(duration, outcome, pollutant1, pollutant2, phase_data) {
  # Fit Survival model
  phase_data$Survial_outcome = Surv(phase_data[[duration]], phase_data[[outcome]])
  
    model.1 <- coxph(formula(paste("Surv(", duration, ", ", outcome, ") ~", pollutant1, "+", pollutant2, "+ nevi + age + factor(sex) + factor(bmi_cat) + factor(smoke)+asthma + diabetes + hyper")), 
               data = phase_data, 
               ties = "breslow")
    
      # Store coefficients and CIs
  HR <- exp(coeftest(model.1, vcov = sandwich)[, 1])
  CI <- exp(confint(coeftest(model.1, vcov = sandwich)))
  
  # Create a data frame with RR and CIs
  result.1 <- as.data.frame(cbind(HR, CI))
  result.1 <- cbind(as.data.frame(rownames(result.1)), result.1)
  names(result.1)[2] <- "HR"
  
 Estimate = result.1[1, "HR"]
  lwr = result.1[1, "2.5 %"]
  upr = result.1[1, "97.5 %"]
 
   Estimate2 = result.1[2, "HR"]
  lwr2 = result.1[2, "2.5 %"]
  upr2 = result.1[2, "97.5 %"] 
  
  result.2<-cbind(Estimate, lwr, upr, Estimate2, lwr2, upr2)
   return(result.2)
}

output<-calculate_adjsurvival_model_multipoll("hospital_days", "death", "no2_avg5", "o3_avg1", coxph_phase1_40cov)
 
```

# E Running all combinations
Note calls to functions require user input of phases, pollutants and outcomes.

```{r}
result_df_s <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        RR = numeric(),
                        lower_95CI = numeric(), 
                        upper_95CI = numeric(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants = c("bc_avg2", "no2_avg5", "pm_avg1")
pollutant2=c("o3_avg1")
duration = "hospital_days"
outcomes = c("discharge", "death") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants)) {
      data = get(phases_data[phase])
      output <- calculate_adjsurvival_model_multipoll(duration, outcomes[outcome], pollutants[pollutant], pollutant2, data)
      
      result_df_s <- rbind(result_df_s, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant = pollutants[pollutant],
                                               Pollutant2=pollutant2,
                                               output))
    }
  }
}

result_df_s
```

#F Run for diabetes
Note calls to functions require user input of phases, pollutants and outcomes.
```{r}
source("L:/dcore-prj0131-SHARED/dcore-prj0131-Stingone/INSIGHT_Jeanette_final/Data Processing2.R")

result_df_d <- data.frame(PhaseData = character(),
                        Outcome = character(),
                        Pollutant = character(),
                        stringsAsFactors = FALSE)

phases_data = c("coxph_phase1_df", "coxph_phase2and3_df", "coxph_phase1_40cov", "coxph_phase2and3_40cov")
pollutants1 = c("bc_avg2", "no2_avg5", "pm_avg1")
pollutant2=c("o3_avg1")
outcomes = c("dialysis") 

for (phase in 1:length(phases_data)) {
  for (outcome in 1:length(outcomes)) {
    for (pollutant in 1:length(pollutants1)) {
      data = get(phases_data[phase])
      output <- calculate_adj_model_multipoll(outcomes[outcome], pollutants1[pollutant], pollutant2, data)
      
      result_df_d <- rbind(result_df_d, data.frame(PhaseData = phases_data[phase],
                                               Outcome = outcomes[outcome],
                                               Pollutant1 = pollutants1[pollutant],
                                               Pollutant2=pollutant2,
                                               output
                                               ))
    }
  }
}

result_df_d
```

## Export in excel workbook

```{r}
require(openxlsx)
list_dataframes <- list("morbidity" = result_df, "dialysis" = result_df_d, "survival"=result_df_s)
write.xlsx(list_dataframes, file = "Adjusted_results_multipoll.xlsx")
```
