---
title: "NYCAS Data Processing"
software: "R v4.2.2"
author: "JAS"
date: "January 19, 2023"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating pollution data by Census tract

This code creates the average pollution values per year for each ZIP Code in NYC, from 2009-2020.

* Using NYCCAS Data released April 2022. Available at: https://data.cityofnewyork.us/Environment/NYCCAS-Air-Pollution-Rasters/q68s-8qxv

* Using 2010 NYC ZCTA Shapefile from GIS Lab at Newman Library, Baruch CUNY. Available at: https://geo.nyu.edu/catalog/nyu-2451-34509

Notes: Code is not very elegant. Could go back and make functions since repeated same steps repeatedly.


```{r dataprep}
#install.packages("rgdal")
#install.packages("raster")
#install.packages("ggplot2")


library(raster)
library(rgdal)
library(ggplot2)
library(sp)
library(sf)
library(dplyr)
library(RColorBrewer)
library(data.table)
library(tidyverse)

# Read this shape file with the rgdal library. 
ct2010<-st_read("C:/users/js5406/Downloads/nyu_2451_34509/nyu_2451_34509.shp")

#Read-in ZCTA file here 

#Read in rastar pollutant files
pm2009<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa1_pm300m/w001001.adf")
bc2009<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa1_bc300m/w001001.adf")
no22009<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa1_no2300m/w001001.adf")
o32009<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s1_o3300m/w001001.adf")
so22009<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w1_so2300m/w001001.adf")

pm2010<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa2_pm300m/w001001.adf")
bc2010<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa2_bc300m/w001001.adf")
no22010<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa2_no2300m/w001001.adf")
o32010<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s2_o3300m/w001001.adf")
so22010<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w2_so2300m/w001001.adf")

pm2011<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa3_pm300m/w001001.adf")
bc2011<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa3_bc300m/w001001.adf")
no22011<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa3_no2300m/w001001.adf")
o32011<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s3_o3300m/w001001.adf")
so22011<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w3_so2300m/w001001.adf")

pm2012<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa4_pm300m/w001001.adf")
bc2012<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa4_bc300m/w001001.adf")
no22012<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa4_no2300m/w001001.adf")
o32012<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s4_o3300m/w001001.adf")
so22012<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w4_so2300m/w001001.adf")

pm2013<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa5_pm300m/w001001.adf")
bc2013<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa5_bc300m/w001001.adf")
no22013<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa5_no2300m/w001001.adf")
o32013<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s5_o3300m/w001001.adf")
so22013<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w5_so2300m/w001001.adf")

pm2014<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa6_pm300m/w001001.adf")
bc2014<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa6_bc300m/w001001.adf")
no22014<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa6_no2300m/w001001.adf")
o32014<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s6_o3300m/w001001.adf")
so22014<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w6_so2300m/w001001.adf")

pm2015<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa7_pm300m/w001001.adf")
bc2015<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa7_bc300m/w001001.adf")
no22015<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa7_no2300m/w001001.adf")
o32015<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s7_o3300m/w001001.adf")
so22015<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w7_so2300m/w001001.adf")

pm2016<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa8_pm300m/w001001.adf")
bc2016<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa8_bc300m/w001001.adf")
no22016<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa8_no2300m/w001001.adf")
o32016<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s8_o3300m/w001001.adf")
so22016<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/w8_so2300m/w001001.adf")

pm2017<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa9_pm300m/w001001.adf")
bc2017<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa9_bc300m/w001001.adf")
no22017<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa9_no2300m/w001001.adf")
o32017<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s9_o3300m/w001001.adf")

pm2018<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa10_pm300m/w001001.adf")
bc2018<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa10_bc300m/w001001.adf")
no22018<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/aa10_no2300m/w001001.adf")
o32018<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/AnnAvg1_10_300mRaster/s10_o3300m/w001001.adf")

pm2019<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/aa11_pm300m/w001001.adf")
bc2019<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/aa11_bc300m/w001001.adf")
no22019<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/aa11_no2300m/w001001.adf")
o32019<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/AnnAvg1_11_300mRaster/s11_o3300m/w001001.adf")

pm2020<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/aa12_pm300m/w001001.adf")
bc2020<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/aa12_bc300m/w001001.adf")
no22020<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/aa12_no2300m/w001001.adf")
o32020<-raster("C:/Users/js5406/Downloads/AnnAvg1_12_300mRaster/s12_o3300m/w001001.adf")
```

### Aggregate raster to ZCTA



```{r agg_ct2010}
int.data<-raster::extract(pm2009, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2009, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22009, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32009, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22009, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.09")
colnames(int.data.bc)<-c("ID", "BC.09")
colnames(int.data.no2)<-c("ID", "NO2.09")
colnames(int.data.o3)<-c("ID", "O3.09")
colnames(int.data.so2)<-c("ID", "SO2.09")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.09", "BC.09", "NO2.09", "O3.09", "SO2.09")

poll.ct2010.09<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2010, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2010, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22010, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32010, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22010, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.10")
colnames(int.data.bc)<-c("ID", "BC.10")
colnames(int.data.no2)<-c("ID", "NO2.10")
colnames(int.data.o3)<-c("ID", "O3.10")
colnames(int.data.so2)<-c("ID", "SO2.10")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.10", "BC.10", "NO2.10", "O3.10", "SO2.10")

poll.ct2010.10<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2011, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2011, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22011, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32011, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22011, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.11")
colnames(int.data.bc)<-c("ID", "BC.11")
colnames(int.data.no2)<-c("ID", "NO2.11")
colnames(int.data.o3)<-c("ID", "O3.11")
colnames(int.data.so2)<-c("ID", "SO2.11")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.11", "BC.11", "NO2.11", "O3.11", "SO2.11")

poll.ct2010.11<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2012, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2012, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22012, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32012, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22012, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.12")
colnames(int.data.bc)<-c("ID", "BC.12")
colnames(int.data.no2)<-c("ID", "NO2.12")
colnames(int.data.o3)<-c("ID", "O3.12")
colnames(int.data.so2)<-c("ID", "SO2.12")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.12", "BC.12", "NO2.12", "O3.12", "SO2.12")

poll.ct2010.12<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2013, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2013, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22013, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32013, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22013, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.13")
colnames(int.data.bc)<-c("ID", "BC.13")
colnames(int.data.no2)<-c("ID", "NO2.13")
colnames(int.data.o3)<-c("ID", "O3.13")
colnames(int.data.so2)<-c("ID", "SO2.13")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.13", "BC.13", "NO2.13", "O3.13", "SO2.13")

poll.ct2010.13<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2014, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2014, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22014, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32014, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22014, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.14")
colnames(int.data.bc)<-c("ID", "BC.14")
colnames(int.data.no2)<-c("ID", "NO2.14")
colnames(int.data.o3)<-c("ID", "O3.14")
colnames(int.data.so2)<-c("ID", "SO2.14")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.14", "BC.14", "NO2.14", "O3.14", "SO2.14")

poll.ct2010.14<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2015, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2015, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22015, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32015, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22015, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.15")
colnames(int.data.bc)<-c("ID", "BC.15")
colnames(int.data.no2)<-c("ID", "NO2.15")
colnames(int.data.o3)<-c("ID", "O3.15")
colnames(int.data.so2)<-c("ID", "SO2.15")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.15", "BC.15", "NO2.15", "O3.15", "SO2.15")

poll.ct2010.15<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2016, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2016, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22016, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32016, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.so2<-raster::extract(so22016, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.16")
colnames(int.data.bc)<-c("ID", "BC.16")
colnames(int.data.no2)<-c("ID", "NO2.16")
colnames(int.data.o3)<-c("ID", "O3.16")
colnames(int.data.so2)<-c("ID", "SO2.16")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

keep.var<-c("ct2010", "PM.16", "BC.16", "NO2.16", "O3.16", "SO2.16")

poll.ct2010.16<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3, int.data.so2)

int.data<-raster::extract(pm2017, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2017, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22017, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32017, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.17")
colnames(int.data.bc)<-c("ID", "BC.17")
colnames(int.data.no2)<-c("ID", "NO2.17")
colnames(int.data.o3)<-c("ID", "O3.17")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3)

keep.var<-c("ct2010", "PM.17", "BC.17", "NO2.17", "O3.17")

poll.ct2010.17<-poll.data.ct2010[,keep.var]
rm(int.data, int.data.bc, int.data.no2, int.data.o3)

int.data<-raster::extract(pm2018, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2018, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22018, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32018, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.18")
colnames(int.data.bc)<-c("ID", "BC.18")
colnames(int.data.no2)<-c("ID", "NO2.18")
colnames(int.data.o3)<-c("ID", "O3.18")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3)

keep.var<-c("ct2010", "PM.18", "BC.18", "NO2.18", "O3.18")

poll.ct2010.18<-poll.data.ct2010[,keep.var]

int.data<-raster::extract(pm2019, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2019, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22019, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32019, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.19")
colnames(int.data.bc)<-c("ID", "BC.19")
colnames(int.data.no2)<-c("ID", "NO2.19")
colnames(int.data.o3)<-c("ID", "O3.19")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3)

keep.var<-c("ct2010", "PM.19", "BC.19", "NO2.19", "O3.19")

poll.ct2010.19<-poll.data.ct2010[,keep.var]

rm(int.data, int.data.bc, int.data.no2, int.data.o3)

int.data<-raster::extract(pm2020, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.bc<-raster::extract(bc2020, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)
int.data.no2<-raster::extract(no22020, ct2010, small = TRUE, fun = mean, na.rm=TRUE, df = TRUE)
int.data.o3<-raster::extract(o32020, ct2010, small = TRUE, fun = mean, na.rm = TRUE, df = TRUE)

colnames(int.data)<-c("ID", "PM.20")
colnames(int.data.bc)<-c("ID", "BC.20")
colnames(int.data.no2)<-c("ID", "NO2.20")
colnames(int.data.o3)<-c("ID", "O3.20")

poll.data.ct2010<-data.frame(ct2010=ct2010$zcta, int.data, int.data.bc, int.data.no2, int.data.o3)

keep.var<-c("ct2010", "PM.20", "BC.20", "NO2.20", "O3.20")

poll.ct2010.20<-poll.data.ct2010[,keep.var]

#poll.int<-merge(poll.ct2010.18, merge(poll.ct2010.17, merge(poll.ct2010.16, merge(poll.ct2010.15, merge(poll.ct2010.14, merge(poll.ct2010.13, merge(poll.ct2010.12, merge(poll.ct2010.11, merge(poll.ct2010.09, poll.ct2010.10, by="ct2010"), by="ct2010"), by="ct2010"), by="ct2010"), by="ct2010"), by="ct2010"), by="ct2010"), by="ct2010"), by="ct2010")


```

### Merge and Export

merge all pollution-year files and save
```{r}
final.poll.data<- list(poll.ct2010.09, poll.ct2010.10, poll.ct2010.11, poll.ct2010.12, poll.ct2010.13, poll.ct2010.14, poll.ct2010.15, poll.ct2010.16, poll.ct2010.17, poll.ct2010.18, poll.ct2010.19, poll.ct2010.20) %>% reduce(left_join, by="ct2010")


write.csv(final.poll.data, file="C:/Users/js5406/Documents/AirPoll_nyczcta_v2.csv")
```



